\textcolor{Navy}{\textsc{Convexity adjustments \`a la Malliavin}}

### 2023-08-04 Latex/paper-resum.tex
# last modificatons in the paper. Fras futures and Fras in arrears.

\begin{example}[Convexity adjustment for futures under the Hull-White model]\label{example_ca_future}
The Cheyette model can be reduced to Hull-White model using the following parameters
\begin{align*}
g(T) &= \exp(-kT), \\
h(t) &= \sigma.
\end{align*}
Moreover, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
\begin{align*}
\eta_s &= \sigma \exp(-ks),\\
\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-ku),\\
\nu(s,t_2) &= \sigma \frac{\exp(-ks) - \exp(-kt_2)}{k}.
\end{align*}
Then the convexity adjustment \eqref{ca_approximation_futures} is
\begin{align*}
CA(t_0,t_1, t_2) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}

@@

\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for FRAs in Arrears is 
\begin{align}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \nonumber \\
&\cdot \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds  + E(t_1).
\end{align}
The error $E(t_1)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{1}{P_{E}(t_1,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_1)$ when $t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty$ when $t_1 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_FRAsinArrears}.
\end{proof}

\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
The model can be restricted to a Hull-White model with constant parameters. The analytical approximation obtained from \eqref{ca_approximations_fra_arrears} is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 + u)) -   \exp(- k(t_2 + u))\Bigr) du 
\end{equation*}
In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$ and $k=0.007$.
\begin{figure}[H]
		\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\end{center}
		\caption{FRA in Arrears: Comparison Malliavin vs MC Simulation}
		\label{fig:FRA_HW}
\end{figure}
\end{example}

@@

\section{Proofs}
\subsection{Proof Theorem \ref{Th_CA_futures}}\label{Proof_CA_futures}
%Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
%\begin{equation}\label{future}
%\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
%\end{equation}
%where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
%\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
%\begin{equation*}
%CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
%\end{equation*}
Note that
\begin{equation*}
CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
\end{equation*}
From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
\begin{equation}\label{girsanov_spot_forward}
dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
\end{equation}
Applying (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
\begin{equation}\label{ca_general_future}
CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left[\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\Bigl[D_s L_{E}(t_0,t_1,t_2) \Bigr] \nu(s,t_2) ds \right]
\end{equation}
where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Calculating the Malliavin derivative of $L_{E}(t_0,t_1,t_2)$ we have that
\begin{equation*}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right).
\end{equation*}
Now from the zero-coupon representation formula (\ref{bond_ois}), we get that
\begin{equation*}
D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
\end{equation*}
Therefore
\begin{equation}\label{malliavin_derive_L}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) }{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
\end{equation}
If we use (\ref{approsimation_E_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k(w)dw \right) \eta(u,x,y)$, we have that
\begin{align*}
D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) \frac{P_{ois}(0,t_2)}{P_{ois}(0,t_0)} - G(t_0,t_1) \frac{P_{ois}(0,t_1)}{P_{ois}(0,t_0)} \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0).
\end{align*}
Therefore
\begin{equation}\label{approximation_clarkocone}
\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \Bigl(G(t_0,t_2)  - G(t_0,t_1)\Bigr)\beta(t,t_0,x_0,\bar{y}_s).
\end{equation}
Then from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we find the approximation for the convexity adjustment for futures.

@@

\subsection{Proof Theorem \ref{Th_CA_FRAsinArrears}}\label{Proof_CA_FRAsinArrears}
$L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$, therefore the expected value of \eqref{FRAinArrear} is taken with respect to the wrong martingale. To calculate the convexity adjustment, we use the Clark-Ocone formula to get a representation for $L_{E}(t_1,t_1,t_2)$, i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\Bigl[L_{E}(t_1,t_1,t_2) \Bigr] + \int_{0}^{t_1} \mathbb{E}^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] dW^{\mathbb{Q}^{t_2}}_{s}.
\end{equation}
Under the HJM dynamics, we have the relation
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + \Bigl(\nu(s,t_2) - \nu(s,t_1)\Bigr) ds. 
\end{equation*}
Taking $\mathbb{E}^{^{t_1}}(\cdot)$, we get that
\begin{align*}
\mathbb{E}^{t_1}\left[L_{E}(t_1,t_1,t_2) \right] &= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left[ \int_{0}^{t_1} \mathbb{E}_s^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2)\Bigr] dW^{t_2}_{s}\right]\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left[ \int_{0}^{t_1} \mathbb{E}_s^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] \Bigl(\nu(s,t_2)-\nu(s,t_1)\Bigr) ds \right].
\end{align*}
Now from (\ref{approximation_D_s_x_t}) we have that 
\begin{eqnarray*}
D_s L(t_1,t_1,t_2) &=& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1}\\
&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\overline{DM}(s,t_1).
\end{eqnarray*}
Using the above approximation, we get
\begin{equation*}
CA(t_0,t_1,t_2) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \int_{0}^{t_1} \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
\end{equation*}
with 
\begin{equation*}
\bar{\nu}(t,t_p, \bar{x}_0(t_a))= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds.   
\end{equation*}

>>>>

\begin{example}[Convexity adjustment for futures under the Hull-White model]\label{example_ca_future}
The Cheyette model can be reduced to Hull-White model using the following parameters
\begin{align*}
g(T) &= \exp(-kT), \\
h(t) &= \exp(k t) \sigma.
\end{align*}
Moreover, from the definition of $g(\cdot)$ and $h(\cdot)$, we have that
\begin{align*}
\eta_s &= \sigma ,\\
\beta(s,u, x_0, \bar{y}_s) &= \sigma \exp(-k(u-s)),\\
\nu(s,t_2) &= \sigma \frac{1 - \exp(-k(t_2-s))}{k}.
\end{align*}
Then the convexity adjustment \eqref{ca_approximation_futures} is
\begin{align*}
CA(t_0,t_1, t_2) & \approx \frac{\sigma^{2} \exp(-k t_0)  P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(\frac{1 - \exp(- k t_0)}{k^{2}} - \frac{t_0 \exp(-k t_2)}{k} \right).   
\end{align*}

@@

\begin{theorem}\label{Th_CA_FRAsinArrears}[Convexity Adjustment approximation for FRAs in Arrears]
Given the Cheyette model in \eqref{short_rate_cheyette}, the hypotheses \ref{boundedness_volatility} and \ref{boundedness_reversion}, and considering the approximations in \eqref{approximation_y_t} and \eqref{approximation_x_t_a}. Then, the convexity adjustment approximation for FRAs in Arrears is 
\begin{align}\label{ca_approximations_fra_arrears}
CA(t_0,t_1) =   &\frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \nonumber \\
&\cdot \int_{0}^{t_1} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds  + E(t_1).
\end{align}
The error $E(t_1)$ is given by (\ref{f_x_y}) with $f(x,y)=\frac{1}{\delta_{t_1,t_2}}\left(\frac{1}{P_{E}(t_1,t_2,x,y)} - 1 \right)$ and behaves as $\mathcal{O}(t_1)$ when $t_1 \to 0$ and $\|E(t_1)\|^{2}_{2} < \infty$ when $t_1 \to \infty$. 
\end{theorem}
\begin{proof}
See appendix \ref{Proof_CA_FRAsinArrears}.
\end{proof}

\begin{example}[Convexity adjustment for FRAs in Arrears under the Hull-White model]\label{example_convexity_hw_FRAsinArrears}
The model can be restricted to a Hull-White model with constant parameters. The analytical approximation obtained from \eqref{ca_approximations_fra_arrears} is
\begin{equation*}
CA(t_0,t_1) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)}  \frac{\sigma^{2}}{k} \int_{0}^{t_1} \Bigl(\exp(- k(t_1 - u)) -   \exp(- k(t_2 - u))\Bigr) \exp(- k(t_1 - u)) du 
\end{equation*}
In Figure \ref{fig:FRA_HW}, we compare the approximation with a Monte Carlo method when the parameters are $\sigma=0.1$ and $k=0.007$.
\begin{figure}[H]
		\begin{center}
		\includegraphics[scale=0.3]{Figures/fra_convexity.jpg}
		\end{center}
		\caption{FRA in Arrears: Comparison Malliavin vs MC Simulation}
		\label{fig:FRA_HW}
\end{figure}
\end{example}

@@

\section{Proofs}
\subsection{Proof Theorem \ref{Th_CA_futures}}\label{Proof_CA_futures}
%Observe that $L_{E}(t, t_1, t_2)$ is a martingale under the forward measure $\mathbb{Q}^{t_2}$. Let us define the future rate as:    
%\begin{equation}\label{future}
%\hat{L}_{E}(t,t_0, t_1, t_2) = \mathbb{E}_t^{\mathbb{Q}}\left[L_{E}(t_0, t_1, t_2) \right]
%\end{equation}
%where $\mathbb{Q}$ is the measure associated to the numeraire $B_t=\exp\left(\int_{0}^{t} r_{ois, s} ds \right)$ with $ r_{ois, t}$ the risk free short rate. Using
%\eqref{forward_rate} and \eqref{future}, then the convexity adjustment definition is
%\begin{equation*}
%CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
%\end{equation*}
Note that
\begin{equation*}
CA(t, t_0, t_1, t_2) = \hat{L}_{E}(t,t_0, t_1, t_2) - \mathbb{E}_t^{\mathbb{Q}^{t_2}}\left[L_{E}(t_0, t_1, t_2) \right].
\end{equation*}
From (\ref{ois_forward_rate_curve}) and since $f_{ois}(t,T)$ is a $\mathbb{Q}^{T}$ martingale, we have that
\begin{equation}\label{girsanov_spot_forward}
dW^{\mathbb{Q}^{t_2}} = dW^{\mathbb{Q}} + \nu(t,t_2) dt. 
\end{equation}
Applying (\ref{general_convexity}) with $f(x_t)=L_{E}(t,t_0, t_1, t_2)$, $\mathbb{Q}_1=\mathbb{Q}$, $\mathbb{Q}_1=\mathbb{Q}^{t_2}$ and $\lambda_t = \nu(t,t_2)$,  we get that
\begin{equation}\label{ca_general_future}
CA(t, t_0, t_1, t_2) = \mathbb{E}^{\mathbb{Q}^{t2}}\left[\int_{0}^{t_0} \mathbb{E}^{\mathbb{Q}}_{s}\Bigl[D_s L_{E}(t_0,t_1,t_2) \Bigr] \nu(s,t_2) ds \right]
\end{equation}
where $\nu(t,T)$ has been defined in (\ref{ois_forward_rate_curve}). Calculating the Malliavin derivative of $L_{E}(t_0,t_1,t_2)$ we have that
\begin{equation*}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)} D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right).
\end{equation*}
Now from the zero-coupon representation formula (\ref{bond_ois}), we get that
\begin{equation*}
D_s \left(\frac{P_{ois}(t_0,t_1)}{P_{ois}(t_0,t_2)}\right) = \frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
\end{equation*}
Therefore
\begin{equation}\label{malliavin_derive_L}
D_s L_{E}(t_0,t_1,t_2) = \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1) }{P^{2}_{ois}(t_0,t_2)} D_s x_{t_0}.
\end{equation}
If we use (\ref{approsimation_E_s_x_t}) with $T_a=t_0$ and $\beta(t,t_0,x,y) = \exp\left(-\int_{s}^{T_a}k(w)dw \right) \eta(u,x,y)$, we have that
\begin{align*}
D_s L_{E}(t_0,t_1,t_2) &\approx \frac{H(t_0,t_1)}{\delta_{t_1,t_2}H(t_0,t_2)}\frac{\partial_{x}P_{ois}(t_0,t_1)P_{ois}(t_0,t_2) - \partial_{x}P_{ois}(t_0,t_2) P_{ois}(t_0,t_1)}{P^{2}_{ois}(t_0,t_2)} \beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0) \nonumber \\
\approx& \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \left(G(t_0,t_2) - G(t_0,t_1) \right)\beta(t,t_0,\bar{x}_s,\bar{y}_s)\bar{M}(s,t_0).
\end{align*}
Therefore
\begin{equation}\label{approximation_clarkocone}
\mathbb{E}_s\left[ D_s L_{E}(t_0,t_1,t_2) \right] = \frac{P_{E}(0,t_1)}{\delta_{t_1,t_2} P_{E}(0,t_2)} \Bigl(G(t_0,t_2)  - G(t_0,t_1)\Bigr)\beta(s,t_0,x_0,\bar{y}_s).
\end{equation}
Then from (\ref{ca_general_future}) and (\ref{approximation_clarkocone}) we find the approximation for the convexity adjustment for futures.

@@

\subsection{Proof Theorem \ref{Th_CA_FRAsinArrears}}\label{Proof_CA_FRAsinArrears}
$L_{E}(t,t_1,t_2)$ is martingale under the measure $\mathbb{Q}^{t_2}$, therefore the expected value of \eqref{FRAinArrear} is taken with respect to the wrong martingale. To calculate the convexity adjustment, we use the Clark-Ocone formula to get a representation for $L_{E}(t_1,t_1,t_2)$, i.e
\begin{equation}\label{general_convexity_fras}
L_{E}(t_1,t_1,t_2) = \mathbb{E}^{t_2}\Bigl[L_{E}(t_1,t_1,t_2) \Bigr] + \int_{0}^{t_1} \mathbb{E}^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] dW^{\mathbb{Q}^{t_2}}_{s}.
\end{equation}
Under the HJM dynamics, we have the relation
\begin{equation*}
dW^{\mathbb{Q}^{t_2}}_s = dW^{\mathbb{Q}^{t_1}}_s + \Bigl(\nu(s,t_2) - \nu(s,t_1)\Bigr) ds. 
\end{equation*}
Taking $\mathbb{E}^{^{t_1}}(\cdot)$, we get that
\begin{align*}
\mathbb{E}^{t_1}\left[L_{E}(t_1,t_1,t_2) \right] &= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left[ \int_{0}^{t_1} \mathbb{E}_s^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2)\Bigr] dW^{t_2}_{s}\right]\\
&= L_{E}(0,t_1,t_2) + \mathbb{E}^{t_1}\left[ \int_{0}^{t_1} \mathbb{E}_s^{t_2}\Bigl[D_s L_{E}(t_1,t_1,t_2) \Bigr] \Bigl(\nu(s,t_2)-\nu(s,t_1)\Bigr) ds \right].
\end{align*}
Now from (\ref{approximation_D_s_x_t}) we have that 
\begin{eqnarray*}
D_s L(t_1,t_1,t_2) &=& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(t_1,t_2)} D_s x_{t_1}\\
&\approx& \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s)\overline{DM}(s,t_1).
\end{eqnarray*}
Using the above approximation, we get
\begin{equation*}
CA(t_0,t_1,t_2) \approx \frac{G(t_1,t_2)}{\delta_{t_1,t_2}P_{E}(0,t_1,t_2)} \int_{0}^{t_1} \beta(s,t_1, \bar{x}_0(t_1), \bar{y}_s) \overline{DM}(s,t_1) \Bigl(\bar{\nu}(s,t_2,\bar{x}_{0}(t_1))-\bar{\nu}(s,t_1,\bar{x}_{0}(t_1))\Bigr) ds
\end{equation*}
with 
\begin{equation*}
\bar{\nu}(t,t_p, \bar{x}_0(t_a))= \int_{t}^{t_p} \eta(s,\bar{x}_0(t_a),\bar{y}_s) ds.   
\end{equation*}
